\textsc{\wobble: a data-driven method for precision radial velocities}

### 2018-12-24 paper/paper.tex
pymc3 + theano references
Former-commit-id: 6e69f649f178d1cded6cfc3890ecf96e04a34928

\software{%
    astropy \citep{Astropy13, Astropy18},
    numpy \citep{Van-Der-Walt:2011},
    matplotlib \citep{Hunter:2007},
    scipy \citep{Jones:2001},
    tensorflow \citep{Abadi15}, 
    exoplanet \citep{exoplanet}
}

>>>>

\software{%
    astropy \citep{Astropy13, Astropy18},
    numpy \citep{Van-Der-Walt:2011},
    matplotlib \citep{Hunter:2007},
    scipy \citep{Jones:2001},
    tensorflow \citep{Abadi15}, 
    exoplanet \citep{exoplanet},
    pymc3 \citep{pymc3},
    theano \citep{theano}
}
